Cycle Route Uptake and Scenario Estimation (CRUSE): an approach for developing strategic cycle network planning tools

### 2024-06-21 paper.qmd
Add zoomed-in view to Figure 4

Other tools that generate areal data to prioritize investment include a study that generated a<span style="color: blue;"> 'bikeability index' for the Metro Vancouver region [@winters_mapping_2013] and later called Bike Score and available for over 160 US and Canadian cities [@winters_bike_2016] -- its methodology is [publicly available](https://www.walkscore.com/bike-score-methodology.shtml); a </span>'prioritization index' for Montreal, Canada [@larsen_build_2013]; a 'usage intensity index' based on stated preferences in Belo Horizonte, Brazil [@zhang_prioritizing_2014]; and a Cycling Potential Tool (CPT) for Scotland [@phillips_development_2017].
The CPT is composed of the base environmental module — based on eight weighted factors (population density, hilliness, physical barriers, access to services, existing cycling mode share, distance to work and school, and road speed) — and the quality of service module, which evaluates each area of interest based on eight factors (surface condition, adjacent cyclists, comfort factor, conflict, distance between junctions, slope, access to services, and origin/destination).

A more recent areal-based approach is the Gross Potential for Cycling (GPC) tool to prioritize areas for cycling infrastructure and other cycling measures  [@silva_gross_2021].
The GPC uses two sets of indicators: population-based indicators (age, potential demand density, employment density and motorization rate) and area-based indicators (accessibility, education, public transport, connectivity, land use mix and relative performance).
These indicators are calculated considering topography, road hierarchy, and average congestion and presented on a scale from 5 to 10.
They are then combined into an overall score, weighted by their impact on cycling according to the literature.
The ranking of areas by the GPC are [publicly available](https://boost.up.pt/en/ferramentas/gpc) and its practical value has been assessed through workshops [@silva_revealing_2022].
<span style="color: blue;">The GPC tool has also been used to investigate the combination of factors contributing to high levels cycling potential [@lopes_impact_2021]. 
Another recent areal-based approach is the Relative Equity Impact of Bicycle Planning (TIRE) [@cunha_assessing_2023]. 
The TIRE assesses the impact of cycling network allocation on the accessibility levels of different socioeconomic groups.</span>

@@

<span style="color: blue;">Another route-based tool is The Cycling Routing Algorithm for Network Connectivity (CRANC) [@gehrke_cycling-focused_2020]. 
The CRANC tool evaluates the benefits of new bicycle facilities for the accessibility of various populations and neighbourhoods. </span>

>>>>

Other tools that generate areal data to prioritize investment include a study that generated a[ 'bikeability index' for the Metro Vancouver region [@winters_mapping_2013] and later called Bike Score and available for over 160 US and Canadian cities [@winters_bike_2016] -- its methodology is [publicly available](https://www.walkscore.com/bike-score-methodology.shtml); a ]{style="color: blue;"}'prioritization index' for Montreal, Canada [@larsen_build_2013]; a 'usage intensity index' based on stated preferences in Belo Horizonte, Brazil [@zhang_prioritizing_2014]; and a Cycling Potential Tool (CPT) for Scotland [@phillips_development_2017].
The CPT is composed of the base environmental module — based on eight weighted factors (population density, hilliness, physical barriers, access to services, existing cycling mode share, distance to work and school, and road speed) — and the quality of service module, which evaluates each area of interest based on eight factors (surface condition, adjacent cyclists, comfort factor, conflict, distance between junctions, slope, access to services, and origin/destination).

A more recent areal-based approach is the Gross Potential for Cycling (GPC) tool to prioritize areas for cycling infrastructure and other cycling measures [@silva_gross_2021].
The GPC uses two sets of indicators: population-based indicators (age, potential demand density, employment density and motorization rate) and area-based indicators (accessibility, education, public transport, connectivity, land use mix and relative performance).
These indicators are calculated considering topography, road hierarchy, and average congestion and presented on a scale from 5 to 10.
They are then combined into an overall score, weighted by their impact on cycling according to the literature.
The ranking of areas by the GPC are [publicly available](https://boost.up.pt/en/ferramentas/gpc) and its practical value has been assessed through workshops [@silva_revealing_2022].
[The GPC tool has also been used to investigate the combination of factors contributing to high levels cycling potential [@lopes_impact_2021]. Another recent areal-based approach is the Relative Equity Impact of Bicycle Planning (TIRE) [@cunha_assessing_2023]. The TIRE assesses the impact of cycling network allocation on the accessibility levels of different socioeconomic groups.]{style="color: blue;"}

@@

[Another route-based tool is The Cycling Routing Algorithm for Network Connectivity (CRANC) [@gehrke_cycling-focused_2020]. The CRANC tool evaluates the benefits of new bicycle facilities for the accessibility of various populations and neighbourhoods. ]{style="color: blue;"}
